Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-27 model.tex
typos in model

 \svdsix     & $ 0.739\pm 0.068 $ & $ 1.438\pm 0.0610$ & $2.197\pm0.083$&  $0.748 \pm 0.011$ \\
  \hline
  \end{tabular}
  \end{center}
 \label{default}
 \caption{MASE scores and weighted permutation entropies for all eight
   processes studied in this paper}
 \label{tab:error}
  \end{table*}%
Comparing these with the geometry of the plots in
Figure~\ref{fig:forecast-example}, one can see some obvious
correspondences.  The average LMA $MASE$ score for the \col signals
was $0.050$, for instance, while ARIMA scored much worse ($0.599$).
That is, LMA performed roughly 20 times better on \col signals than a
random-walk predictor, while ARIMA only outperformed random walk by a
factor of 1.7.  This is in accordance with the
visual appearance of the corresponding images in
Figure~\ref{fig:forecast-example}.  While the correspondence between
$MASE$ score and the visual appearance of a $p$ versus $c$ plot is
clear cut in this case, that is not always so.  The plots of LMA
predictions of \col and \svdfive both lie near the diagonal, for
instance, but the corresponding $MASE$ scores were very different:
$0.050$ for \col and $0.718$ for \svdfive (resp., 20 and 1.4 times
better than random-walk forecasts of the same signals).  This is a
result of the normalization in the $MASE$ score.  Recall from
Section~\ref{sec:simple} that the random-walk method performs
especially poorly on signals that oscillate rapidly.  \col fits this
description, so the random-walk error on this signal---the denominator
of the three $MASE$ scores in the first row of the Table---is
pathologically high, which skews those scores down.  Random-walk
prediction is very effective for the \svdfive signal, on the other
hand, so the denominator is small and the $MASE$ scores are skewes
upwards.  Normalization is, as is often the case, a two-edged sword.
Here, it facilitates comparisons across signals of different types and
lengths, but its particular pathologies must be taken into account, as
discussed at more length in Section~\ref{sec:results}.

>>>>

 \svdsix     & $ 0.739\pm 0.068 $ & $ 1.438\pm 0.0610$ & $2.197\pm0.083$&  $0.748 \pm 0.011$ \\
  \hline
  \end{tabular}
  \end{center}
 \label{default}
 \caption{MASE scores and weighted permutation entropies for all eight
   processes studied in this paper}
 \label{tab:error}
  \end{table*}%
Comparing these with the geometry of the plots in
Figure~\ref{fig:forecast-example}, one can see some obvious
correspondences.  The average LMA $MASE$ score for the \col signals
was $0.050$, for instance, while ARIMA scored much worse ($0.599$).
That is, LMA performed roughly 20 times better on \col signals than a
random-walk predictor, while ARIMA only outperformed random walk by a
factor of 1.7.  This is in accordance with the
visual appearance of the corresponding images in
Figure~\ref{fig:forecast-example}.  While the correspondence between
$MASE$ score and the visual appearance of a $p$ versus $c$ plot is
clear cut in this case, that is not always so.  The plots of LMA
predictions of \col and \svdfive both lie near the diagonal, for
instance, but the corresponding $MASE$ scores were very different:
$0.050$ for \col and $0.718$ for \svdfive (resp., 20 and 1.4 times
better than random-walk forecasts of the same signals).  This is a
result of the normalization in the $MASE$ score.  Recall from
Section~\ref{sec:simple} that the random-walk method performs
especially poorly on signals that oscillate rapidly.  \col fits this
description, so the random-walk error on this signal---the denominator
of the three $MASE$ scores in the first row of the Table---is
pathologically high, which skews those scores down.  Random-walk
prediction is very effective for the \svdfive signal, on the other
hand, so the denominator is small and the $MASE$ scores are skewed
upwards.  Normalization is, as is often the case, a two-edged sword.
Here, it facilitates comparisons across signals of different types and
lengths, but its particular pathologies must be taken into account, as
discussed at more length in Section~\ref{sec:results}.
